Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-02-08 draft.tex
new figures and changes to the methods section

			explanation is in the following section. Figure \ref{fig:model_plot} represents the
			layout of the model layers.

@@

					\includegraphics[width=1\textwidth]{images/model_plot.png}
					\caption{The architecture of the model used for the experiment.}

@@

@@

			each sample and an upper limit of 1,000,000 lines per batch. For each batch, two
			epochs were performed. Because a single sample can have multiple input lines,
			evaluation cannot be performed on a per-line basis, but must instead be summarized.
			Two methods are possible: median and mean, with the difference in results being
			negligible in our experiments. The default threshold is 0.5, meaning that a result
			under 0.5 is a false result and over 0.5 is a true result. This threshold can however
			be adjusted, useful for computing the EER.

>>>>

			explanation is in the following section. Figure \ref{fig:model_plot} depicts the
			general structure of the model, with the submodel components being connected to the
			terminus model for final processing. Figures \ref{fig:mel_model_plot} and
			\ref{fig:term_model_plot} offer a further look into the architecture, being an example
			of one submodel, specifically the submodel for the mel-spectrogram feature, as well as
			a look into a terminus model with three hidden layers respectively.

@@

					\includegraphics[width=0.7\textwidth]{images/model_fig.png}
					\caption{The general architecture format for the models used in these
					experiments. In every feature, as well as in the terminus, there can be
					various kinds of hidden layers.}

@@

					\includegraphics[width=0.4\textwidth]{images/mel_model_plot.png}
					\caption{Example of a submodel for the mel-spectrogram features, including the
					hidden layers and output sizes.}
					\label{fig:mel_model_plot}
					\includegraphics[width=0.4\textwidth]{images/term_model_plot.png}
					\caption{Example of a terminus model with three hidden layers.}
					\label{fig:term_model_plot}

@@

			each sample and an upper limit of 1,000,000 lines per batch. For each batch, either
			one or two epochs were performed. Because a single sample can have multiple input
			lines, evaluation cannot be performed on a per-line basis, but must instead be
			summarized. Two methods are possible: median and mean, with the difference in results
			being negligible in our experiments. The default threshold is 0.5, meaning that a
			result under 0.5 is a negative result and over 0.5 is a positive result. This
			threshold can however be adjusted, useful for computing certain metrics.
